### 2013-12-11 Publications/2013-TMI/03-introduction.tex
Fixed some references
Added Alessandro's paper on TMI about ISBI13

\IEEEPARstart{D}{iffusion} \gls{mri} is a widely used family
of \gls{mri} techniques \citep{sundgren_diffusion_2004} which 
accounts for a growing interest in its application to structural 
connectivity analyses of the brain at the macro-scale
\citep{craddock_imaging_2013}. This emerging field exploits
\gls{dwi} data to derive the local axonal structure at each imaging voxel 
\citep{basser_microstructural_2011} and estimate a whole-brain mapping of fiber 
tracts \citep{hagmann_mr_2012,johansen-berg_using_2009} represented by 
trajectories reconstructed from the local information.
This comprehensive map of neural connections of the brain is called the 
\emph{connectome} \citep{hagmann_diffusion_2005,sporns_human_2005}. The connectome
analysis is a promising tool for neuroscience \citep{morgan_why_2013} and 
for the clinical application \citep{griffa_structural_2013} as well.

@@

After correcting for artifacts, the difficulty of performing analyses directly
on the \emph{directionally dependent} raw data is not affordable. Thus, 
\gls{dwi} data is reconstructed using one of a numerous set of readily 
available algorithms. The outcome is a voxel-wise model of diffusion shape 
(in \citep{daducci_isbi2013_2013} \todo{FIX ref} there is available a comprehensive review of 
state-of-art methodologies). On top of the
chosen model, some scalar maps describing tissue features are generally
computed (e.g. \gls*{fa}, and \gls*{adc}).
%For instance, the most popular \gls{dwi}-derived scalar map 
%is \gls{fa} which depicts the isotropy of water diffusion inside the brain.
%Another widely studied map is the \gls{adc} (or \gls{md} that has a dual definition),
%which reflects the intensity of the diffusion effect. Many other
%directionally invariant measurements have been defined. For a comprehensive study, 
%we refer to \citep{ennis_orthogonal_2006}.

@@

One approach to correcting the susceptibility distortions was proposed
with the earliest \gls{epi} sequences used in functional \gls{mri}, and
relies on the acquisition of extra \gls{mri} data. Generally, a \gls{gre} is used to 
obtain a map of magnitude and phase of the actual magnetic field inside the
scanner. Based on this \emph{fieldmap} and the theory underlying the 
distortion, \citep{jezzard_characterization_2005} proposed a correction 
methodology. A number of forked and improved methodologies have been 
developed to correct for the susceptibility distortion and received the
generic name of ``fieldmap correction'' techniques \cite{hsu_correction_2009,
reber_correction_2005}.

>>>>

\IEEEPARstart{D}{iffusion} \gls{mri} is a widely used family
of \gls{mri} techniques \citep{sundgren_diffusion_2004} which 
accounts for a growing interest in its application to structural 
connectivity analyses of the brain at the macro-scale
\citep{craddock_imaging_2013}. This emerging field exploits
\gls{dwi} data to derive the local axonal structure at each imaging voxel 
\citep{basser_microstructural_1996} and estimate a whole-brain mapping of fiber 
tracts \citep{hagmann_mr_2012,johansen-berg_using_2009} represented by 
trajectories reconstructed from the local information.
This comprehensive map of neural connections of the brain is called the 
\emph{connectome} \citep{hagmann_diffusion_2005,sporns_human_2005}. The connectome
analysis is a promising tool for neuroscience \citep{morgan_why_2013} and 
for the clinical application \citep{griffa_structural_2013} as well.

@@

After correcting for artifacts, the difficulty of performing analyses directly
on the \emph{directionally dependent} raw data is not affordable. Thus, 
\gls{dwi} data is reconstructed using one of a numerous set of readily 
available algorithms. The outcome is a voxel-wise model of diffusion shape 
(\citep{daducci_quantitative_2013} contains a comprehensive review of 
state-of-art methodologies). On top of the
chosen model, some scalar maps describing tissue features are generally
computed (e.g. \gls*{fa}, and \gls*{adc}).
%For instance, the most popular \gls{dwi}-derived scalar map 
%is \gls{fa} which depicts the isotropy of water diffusion inside the brain.
%Another widely studied map is the \gls{adc} (or \gls{md} that has a dual definition),
%which reflects the intensity of the diffusion effect. Many other
%directionally invariant measurements have been defined. For a comprehensive study, 
%we refer to \citep{ennis_orthogonal_2006}.

@@

One approach to correcting the susceptibility distortions was proposed
with the earliest \gls{epi} sequences used in functional \gls{mri}, and
relies on the acquisition of extra \gls{mri} data. Generally, a \gls{gre} is used to 
obtain a map of magnitude and phase of the actual magnetic field inside the
scanner. Based on this \emph{fieldmap} and the theory underlying the 
distortion, \citep{jezzard_correction_1995} proposed a correction 
methodology. A number of forked and improved methodologies have been 
developed to correct for the susceptibility distortion and received the
generic name of ``fieldmap correction'' techniques \cite{hsu_correction_2009,
reber_correction_1998}.
